% School Projects
\begin{works}[\schoolProject]
\setLanguageValues[\nowLanguage]{
  \workItem{Parallelization applications}{Dublin, Ireland}{Postgraduate Thesis}{Dec. 2010 -- Aug. 2011}{
    \resitem{Title: Parallelisation and application of terrain propagation models}
    \resitem{Implemented the codes in C++ template with OpenMP \& OpenMPI}
    \resitem{Rewrite the codes in Erlang}
    \resitem{Analysis the PThread's implementation of OpenMP, Erlang}
    \resitem{Study the operation of Supercomputers: qsub}
    \resitem{\href{http://code.google.com/p/wpcdcuassignment2010-2011/downloads/detail?name=CB28FinalReport.pdf}{Final Report}}
  }

  \workItem{OpenGL Solar system}{Dublin, Ireland}{Graphics and Visualisation Assignment}{Mar. 2011 -- Apr. 2011}{
    \resitem{Write the codes in C++ OpenGL on Linux \& Windows}
    \resitem{Know the detail about OpenGL Framework:Main loop, invoke functions, Matrix stacks}
    \resitem{Write the Scene Graph by myself}
    \resitem{\href{http://code.google.com/p/wpcdcuassignment2010-2011/downloads/detail?name=EE563Assignment02Report.pdf}{Final Report}}
  }

  \workItem{Java 3D Flight Game}{Dublin, Ireland}{Graphics and Visualisation Assignment}{Feb. 2011 -- Mar. 2011}{
    \resitem{Title: Java 3D Flight Game}
    \resitem{Use the Java 3D API}
    \resitem{Study the basic knowledge about Graphics and Visualisation technicals}
    \resitem{Use the Scene Graph, Java Behaviors}
    \resitem{\href{http://code.google.com/p/wpcdcuassignment2010-2011/downloads/detail?name=EE563Assignment01report.pdf}{Final Report}}
  }

  \workItem{Packet Event Simulator}{Dublin, Ireland}{Data Network Protocol Analysis \& Simulation Assignment}{Nov. 2010 -- Dec. 2010}{
    \resitem{Title: Discrete-Event Simulation of a Packet-Switched Network}
    \resitem{Write Program in Erlang \& Java}
    \resitem{Use the Time driving and Event driving}
    \resitem{\href{http://code.google.com/p/wpcdcuassignment2010-2011/downloads/detail?name=EE509Assignment1-report.pdf}{Final Report}}
  }

  \workItem{Java RMI application}{Dublin, Ireland}{Network Programming Assignment}{Nov. 2010 -- Dec. 2010}{
    \resitem{Title: Java RMI Library manage application}
    \resitem{Write in Java}
    \resitem{Use Java Swing, Java AWT, Java RMI}
    \resitem{\href{http://code.google.com/p/wpcdcuassignment2010-2011/downloads/detail?name=EE562-networkProgramming-Assignment-Report.pdf}{Final Report}}
  }

  \workItem{ITS}{Wuhan, China}{Undergraduate Thesis}{Jan. 2010 -- Jun. 2010}{
    \resitem{Designed and implemented the simulation system for the basic traveling by Java Drawing. Learned the Java Drawing, GUI Structure.}
    \resitem{Designed the System interface between each part. Learned the communication by TCP/IP in linux.}
    \resitem{Implemented the information collecting module under ARM9. Learned how to program in ARM9, the Linux system administer and DHCP communication.}
    \resitem{Designed the information analysis under BP-Neural network by matlab. Learned the basic knowledge about AI.}
  }

  \workItem{Web Server}{Wuhan, China}{The project of 'Computer Network'}{Aug. 2009 -- Sep. 2009}{
    \resitem{Designed and implemented the server by C. Learned the details about the HTTP1.1, make and Linux network programming.}
  }

  \workItem{Greedy Snake game in C51}{Dalian, China}{Summer Training}{Jun. 2009 -- Jul. 2009}{
    \resitem{Designed the system. Learned the designing methods for Embedded System, $\mu$C/OS and C51}
    \resitem{Implemented the communication between each module.}
  }

  \workItem{CMM Interpreter}{Wuhan, China}{The project of 'Compiler theory'}{Oct. 2008 -- Jan. 2009}{
    \resitem{Designed and implemented the Interpreter by Java. Learned the LL(1) syntax parser, XML configuration for DFA and a Java Console environment.}
  }

  \workItem{Students Blogger System}{Wuhan, China}{Summer Training}{Jul. 2008 -- Aug. 2008}{
    \resitem{As a leader of the team with eleven. Learned how to manage the team by responsibility and report to teachers.}
    \resitem{Designed and implemented the Articles classified Module for the Blogger System. Learned how to classify article by keywords and Segmentation for Chinese words.}
  }

  \workItem{School Room management System}{Wuhan, China}{The project of 'Database system lesson'}{May. 2008}{
    \resitem{Designed and implemented a login template system for my classmates. Learned the XML config and the framework for configuration.}
    \resitem{Designed and implemented an auto-generated application for iBatis-ORM. Learned the auto-work concept, and Cross-platform methods.}
    \resitem{Taught my classmates how to finish the project. Learned how to communicate, teach and encourage.}
    \resitem{Manage my team of ten. Learned how to communicate with partners, allocate works.}
  }

  \workItem{School Voting System}{ISS, Wuhan University}{For school Excellent Student Awarding}{Dec 2007}{
    \resitem{Designed a voting system for college students.Learned Design Patterns for JAVA.}
    \resitem{Implemented the system. Learned iBatis, JSP, MySQL, Linux, Apache HTTP, Tomcat.}
  }
}{

   \workItem{并行重构电磁波模型代码}{都柏林城市大学}{硕士毕业论文}{2010.12 -- 2011.08}{
     \resitem{将代码利用Erlang, C++进行重构}
     \resitem{学习了超级计算机的控制管理技术}
     \resitem{分析学习了OpenMP、Erlang的多线程部分实现}
     \resitem{\href{http://code.google.com/p/wpcdcuassignment2010-2011/downloads/detail?name=CB28FinalReport.pdf}{最终报告}}
   }

%  \workItem{OpenGL 太阳系模拟系统}{都柏林城市大学}{图像与视觉技术作业}{2011.03 -- 2011.04}{
%    \resitem{在Windows与Linux上利用OpenGL API 编写}
%    \resitem{深入理解了 OpenGL 结构: 驱动框架, 各种钩子函数, 矩阵栈}
%    \resitem{手动实现了符合系统需要的 Scene Graph }
%    \resitem{\href{http://code.google.com/p/wpcdcuassignment2010-2011/downloads/detail?name=EE563Assignment02Report.pdf}{最终报告}}
%  }
%
%  \workItem{Java 3D 飞行游戏}{都柏林城市大学}{图像与视觉技术作业}{2011.02 -- 2011.03}{
%    \resitem{学习并使用了Java 3D API}
%    \resitem{加深了对3D图像处理的理解和认识}
%    \resitem{学习使用了Scene Graph, Java Behaviors}
%    \resitem{\href{http://code.google.com/p/wpcdcuassignment2010-2011/downloads/detail?name=EE563Assignment01report.pdf}{最终报告}}
%  }

  \workItem{数据包模拟器}{都柏林城市大学}{课程作业}{2010.11 -- 2010.12}{
    \resitem{名字: 数据包交换网络的离散事件模拟程序}
    \resitem{利用 Erlang \& Java 语言实现}
    \resitem{采用了事件驱动与时间驱动}
    \resitem{\href{http://code.google.com/p/wpcdcuassignment2010-2011/downloads/detail?name=EE509Assignment1-report.pdf}{最终报告}}
  }

  \workItem{Java RMI 程序}{都柏林城市大学}{网络编程作业}{2010.11 -- 2010.12}{
    \resitem{Title: Java RMI 图书馆管理系统}
    \resitem{利用Java编写}
    \resitem{使用了 Java Swing, Java AWT, Java RMI}
    \resitem{\href{http://code.google.com/p/wpcdcuassignment2010-2011/downloads/detail?name=EE562-networkProgramming-Assignment-Report.pdf}{最终报告}}
  }

  \workItem{智能交通系统模型}{武汉大学}{本科毕业论文}{2010.01 -- 2010.06}{
    \resitem{设计实现了智能交通模拟系统。从中学习到了模拟技术的基本解决方法}
    \resitem{设计了车辆前端与服务器交互模块。从中学习到了嵌入式Linux网络开发}
    \resitem{设计了给予神经网络的分析模块。了解了神经网络在智能交通领域的相关知识}
  }

  \workItem{Web服务器}{武汉大学}{计算机网络实践课作业}{2009.08 -- 2009.09}{
    \resitem{设计并开发了基于HTTP1.1的简单Web服务器。从中学习到了基于自动机的协议分析技术与Linux服务器端编程技术}
  }

  \workItem{基于C51的贪吃蛇游戏}{中国大连}{大三暑期实训}{2009.06 -- 2009.07}{
    \resitem{设计了整个游戏系统。从中学习到了嵌入式开发技术与$\mu{}C/OS$}
    \resitem{开发了系统中控模块。学习到了事件驱动设计模式}
  }

  \workItem{CMM解析器}{武汉大学}{编译原理编程实践}{2008.10 -- 2009.01}{
    \resitem{设计并实现了基于Java的C语言解析器。学习到了LL(1)语法分析技术，给予XML可配置的DFA分析器以及Java终端模式控制器}
  }

%  \workItem{学生Blog系统}{武汉大学}{大二暑期实训}{2008.07 -- 2008.08}{
%    \resitem{作为整个团队的经理。学习了如何更好地与队员们沟通并协调各方工作以及如何更好的向老师汇报}
%    \resitem{设计并开发了文章相关性分析模块。学习到了基于字典的中文分词技术与相关性文章分析技术}
%  }

%  \workItem{学生宿舍管理系统}{武汉大学}{数据库课程设计}{2008.05}{
%    \resitem{设计实现了可配置的登录验证模块，方便全班同学进行开发。更深刻地理解了Servlet/Filter设计模式与思想}
%    \resitem{设计实现了基于IBatis的ORM可配置生成框架。学习到了自动生成技术}
%    \resitem{向同学们讲授JSP/Servlet基本开发技术。从中学习到了如何向同学们传授知识}
%    \resitem{管理本小组开发团队。学习到了如何更好地和组员进行交流。}
%  }
%
%  \workItem{国软之星投票系统}{武汉大学}{用于武汉大学国际软件学院国软之星活动投票}{2007.10}{
%    \resitem{设计并开发了投票系统。学习到了JSP/Servlet，Tomcat部署，iBatis}
%  }
}
\end{works}
